\sc Building sex-specific synthetic lethality network in cancer - Temp Name

### 2023-07-20 sl_report_pmcrc/paper0904.tex
updates to report

	RNA sequencing (RNA-seq) data was obtained from The Cancer Genome Atlas (TCGA). Raw STAR aligned counts for tumor tissue and healthy tissue samples were utilized. The Cancer Genome Atlas contains genomic information which spans 33 cancer types. For the purpose of this study, only 12 of the 33 cancer types were considered. We first filtered out sex-biased cancers which include breast invasive carcinoma (BRCA), cervical cell carcinoma (CESC), ovarian serous cystadenocarcinoma (OV), prostate adenocarcinoma (PRAD), testicular germ cell tumors (TGCT), uterine corpus endometrial carcinoma (UCEC), and uterine carcinosarcoma (UCS). Next, we filtered out blood cancers as well as cancers which lacked normal tissue gene expression samples. This included adrenocortical carcinoma (ACC), lymphoid neoplasm diffuse large b-cell lymphoma (DLBC), glioblastoma multiforme (GBM), acute myeloid leukemia (LAML), and brain lower grade glioma (LGG). Finally, we filtered out cancers that did not have any matching pairs of samples (NT and TP from same individual), as well as cancers that had extremely low numbers of matched sample pairs. This included mesothelioma (MESO), skin cutaneous melanoma (SKCM), thymoma (THYM), uveal melanoma (UVM), cholangiocarcinoma (CHOL), pancreatic adenocarcinoma (PAAD), pheochromocytoma and paraganglioma (PCPG), rectum adenocarcinoma (READ), and sarcoma (SARC).

@@

>>>>

	RNA sequencing (RNA-seq) data was obtained from The Cancer Genome Atlas (TCGA). Raw STAR (Spliced Transcripts Alignment to a Reference) aligned counts for tumor tissue and healthy tissue samples were collected. The Cancer Genome Atlas contains genomic information which spans 33 cancer types. For the purpose of this study, only 12 of the 33 cancer types were considered. We first filtered out sex-biased cancers which include breast invasive carcinoma (BRCA), cervical cell carcinoma (CESC), ovarian serous cystadenocarcinoma (OV), prostate adenocarcinoma (PRAD), testicular germ cell tumors (TGCT), uterine corpus endometrial carcinoma (UCEC), and uterine carcinosarcoma (UCS). The reason for this was due to the fact that we are already aware of sex biases in these cancer types. Next, we filtered out blood cancers as well as cancers which lacked normal tissue gene expression samples. This included adrenocortical carcinoma (ACC), lymphoid neoplasm diffuse large b-cell lymphoma (DLBC), glioblastoma multiforme (GBM), acute myeloid leukemia (LAML), and brain lower grade glioma (LGG). The reason for this was due to the fact that we did not have adequate control samples to compare to tumor samples. Finally, we filtered out cancers that did not have any matching pairs of samples (NT and TP from same individual), as well as cancers that had less than 10 matched sample pairs across both males and females. This included mesothelioma (MESO), skin cutaneous melanoma (SKCM), thymoma (THYM), uveal melanoma (UVM), cholangiocarcinoma (CHOL), pancreatic adenocarcinoma (PAAD), pheochromocytoma and paraganglioma (PCPG), rectum adenocarcinoma (READ), and sarcoma (SARC). We selected matched tumor-normal sample pairs to help control for genetic background and other individual-specific factors that could influence gene expression. Once cancer types were selected, two pan-cancer raw count gene expression matrices were created, one for males and one for females.

@@

	Raw count gene expression matrices for males and females were pre-filtered to remove genes unlikely to exhibit differential expression. For each matrix, we calculated the 90th quantile of overall gene expression as a threshold. For each gene in the matrix, we checked to see whether its expression was greater than the threshold in at least 1 sample, and removed genes where no samples showed expression greater than the quantile threshold.
